logbook simulations

### 2020-03-17 datasets/data_preprocessing.nb.Rmd
udpate simulation

```{r}
# create test dataset
w_test <- w_asr %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  filter(abstract != "") %>%
  distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts

>>>>

```{r}
# create test dataset
w_test <- w_asr %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  filter(abstract != "",
         abstract!= " ") %>
  distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts

### 2020-03-17 simulation/README.Rmd
udpate simulation

```{r include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
```

```{r, echo = FALSE}
conditiongrid <- readRDS("00_conditiongrid.RDS")

conditiongrid$condition %>%
  kable(format = "markdown") %>%
  pack_rows("Classifier", 1, 5) %>%
  pack_rows("Feature Extraction", 6, 10) %>%
  pack_rows("Balance Strategy", 11, 20)
```

@@

@@

# Stage 1 - Classifiers 
Comparing five different classifiers
```{r}
hyperparametersets <- readRDS("01_hyperparameter_sets.RDS")

hyperparametersets %>%
  kable(format = "markdown")
```

@@

### 1.1.1 Ace
```{r}
lubridate::date("2020-03-17")
```

@@

Optimization run on Cartesius
```{bash, eval = FALSE}
# RCTW
./cart_hyper_run.py hyper-active -t 10 -m rf -b double -e tfidf -q max -d ace

@@

>>>>

```{r include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE)
```

```{r}
conditiongrid <- readRDS("00_conditiongrid.RDS")

conditiongrid %>%
  kable(format = "markdown")
```

@@

asreview

@@

# Stage 1 - Classifiers 
Comparing five different classifiers
```{r}
hyperparametersets <- readRDS("01_hyperparameter_sets.RDS")
```

@@

### 1.1.1 Ace

```{r}
lubridate::date("2020-03-17")
```

@@

Optimization run on Cartesius
```{bash, eval = FALSE}
# RCTW
./cart_hyper_run.py hyper-active -t 5 -m rf -b double -e tfidf -q max -d ace -r 23

@@

```{r}
# to-do grid 
todo <- hyperparametersets

# set emojis for grid 
c <- emo::ji("check")

todo$ace[1] <- c
```

```{r}
# save the to-do grid in markdown style
todo <- todo %>%
  kable(format = "markdown")
saveRDS(todo, file = "02_todo_hp.RDS")

todo 
```
